Exact asymptotic expressions for local clustering in hyperbolic random graphs \\ \TM{ I prefer not to use the term ``hyperbolic random graph". Better : KPKVB random graph or, in the title,``a hyperbolic model of complex networks"}

### 2019-01-10 clustering_infinite_model.tex
Merging Tobias' comments

In this section we will establish the exact expressions for the limit local clustering coefficient and function, $c_\Pcal$ and $c_{\Pcal}(k)$, respectively. This is done in several steps. Recall that for $p\in \R \times \R_+ := \Rcal$,
\[
	\BallPo{p} = \{p^\prime \in \R \times \R_+ : |x - x^\prime| \le e^{\frac{y + y^\prime}{2}}\},
\]
denotes the neighborhood ball of $p$. Furthermore we recall the definition of $\Delta_\Pcal$ 
\[
	\Delta_{\Pcal}(y) = \iint_{\Rcal^2} T_\Pcal(p,p_1,p_2) \eta_{y}(x_1,y_1)\eta_{y}(x_2,y_2) \, dx1 \, dx_2 \, dy_1 \, dy_2,
\]
where $\eta_{y} = \frac{\mu_{\alpha,\nu}|_{\BallPo{(0,y)}}}{\Mu{\BallPo{(0,y)}}}$ is the marginal probability density associated with a randomly sampled neighbor of $(0,y)$.

@@

Before we analyze local clustering in the infinite limit model, we first establish some results for its degree distribution. We define the probability distribution for the degree of node $p = (x,y)$ as
\begin{equation}
	\rho(p,k) = \Prob{D_\Pcal(p) = k} = \Prob{\Po(\mu_{\alpha,\nu}(\BallPo{p})) = k},
\end{equation}
where $\Po(\lambda)$ denotes a Poisson random variable with mean $\lambda$. Recall from equation \eqref{eq:mu_ball_y_P} that
\[
	\mu_{\alpha,\nu}(\BallPo{p}) = \xi_{\alpha,\nu} e^{\frac{y}{2}},
\]
only depends on the $y$-coordinate of $p$. Therefore, we will often write $\rho(y,k)$ instead of $\rho(p,k)$.

@@

Since $\Gamma^{+}(k-2\alpha, \xi_{\alpha,\nu})/\Gamma(k - 2\alpha) \sim k^{-(2\alpha+1)}$ as $k \to \infty$ \PvdH{@All: Does anyone have a good standard reference for this?} we deduce that
\begin{equation}\label{eq:degree_distribution_P_asymptotics}
	\Prob{D_\Pcal = k} \sim 2\alpha (\xi_{\alpha,\nu})^{2\alpha} k^{-(2\alpha + 1)}
	\quad \text{as } k \to \infty.
\end{equation}

By a similar computation we have the following result, which will be useful later on. For any $\beta > 0$, as $k \to \infty$
\begin{equation}\label{eq:general_integral_rho_y_k}
	\int_0^\infty e^{\beta y} \rho_y(k) \alpha e^{-\alpha y} \, dy
    \sim 2\alpha \left(\xi_{\alpha,\nu}\right)^{2(\beta + \alpha)} k^{-2(\beta + \alpha)-1}.
\end{equation}

@@

The proof of this proposition is involved and technical. We therefore postpone it till Section \ref{ssec:asymptotics_Delta_y_P} and first use it to prove Theorem \ref{thm:asymptotics_average_clustering_P}.

@@

We only give the proof for the case $\frac{1}{2} < \alpha < \frac{3}{4}$. The proofs for the other two cases are similar. Let $\varphi_1(y)$ be defined as in Proposition \ref{prop:asymptotics_Delta_y_P} and define
\[
	\epsilon_1(k) = \int_0^{\infty} \varphi_1(y) e^{-(4\alpha - 2)\frac{y}{2}} \rho(y,k) \alpha e^{-\alpha y} \dd y
\]
Then we have that
\[
	\int_0^{\infty} \Delta_{\mathcal{P}}(y) \rho(y,k) \alpha e^{-\alpha y} \dd y
	= C_\alpha \int_0^{\infty} e^{-(4\alpha - 2)\frac{y}{2}} \rho(y,k) \alpha e^{-\alpha y} \dd y + \epsilon_1(k).
\]

Using \eqref{eq:general_integral_rho_y_k} with $\beta = 2\alpha - 1$ yields,
\begin{equation}\label{eq:asymptotics_clustering_integral}
	\int_0^{\infty} e^{-(4\alpha - 2)\frac{y}{2}} \rho(y,k) \alpha e^{-\alpha y} \dd y 
	\sim 2\alpha \xi_{\alpha,\nu}^{6\alpha - 2} k^{-(6\alpha - 1)},
\end{equation}
as $k \to \infty$. Therefore, by applying the asymptotic scaling for the denominator~\eqref{eq:degree_distribution_P_asymptotics} we get
\begin{align*}
	c_\infty(k) &= \frac{\int_0^{\infty} \Delta_{\mathcal{P}}(y) \rho(y,k) \alpha  e^{-\alpha y} \dd y}
		{\int_0^\infty \rho_{y}(k) \alpha e^{-\alpha y} \dd y} \\
	&\sim C_\alpha 2\alpha \xi_{\alpha,\nu}^{4\alpha - 2} \frac{k^{-(6\alpha - 1)}}{k^{-(2\alpha - 1)}}
	+ \frac{\epsilon_1(k)}{2\alpha \xi_{\alpha,\nu}^{2\alpha} k^{-(2\alpha - 1)}}\\
	&= C_\alpha 2\alpha \xi_{\alpha,\nu}^{4\alpha - 2} k^{-4\alpha + 2} 
    + \frac{1}{2\alpha}\xi_{\alpha,\nu}^{-2\alpha} k^{2\alpha - 1}\epsilon_1(k).
\end{align*}
Hence, to prove the result it is enough to show that
\[
	\lim_{k \to \infty} k^{6\alpha - 3}\epsilon_1(k) = 0.
\]
For this we fix $0 < \varphi < 1$, define $a(k) = 2\log((1-\varphi)k)$ and split the integral into two pieces
\begin{align*}
	\epsilon_1(k) &= \int_0^{\infty} \varphi_1(y) e^{-(4\alpha - 2)\frac{y}{2}} \rho(y,k) \alpha e^{-\alpha y} \dd y\\
	&= \int_0^{a(k)} \varphi_1(y) e^{-(4\alpha - 2)\frac{y}{2}} \rho(y,k) \alpha e^{-\alpha y} \dd y\\
	&\hspace{10pt}+ \int_{a(k)}^{\infty} \varphi_1(y) e^{-(4\alpha - 2)\frac{y}{2}} 
    	\rho(y,k) \alpha e^{-\alpha y} \dd y.
\end{align*} 
For the first integral we use that $\rho(y,k)$ is increasing on $[0,a(k)]$ and
\[
	k^{6\alpha - 3}\rho(a(k),k) = O\left(\frac{k^{6\alpha - 3 + (1-\varphi)k}}{k!} e^{-(1-\varphi)k}\right) = o(1),
\]
to obtain
\begin{align*}
	&\hspace{-30pt}\lim_{k \to \infty} k^{6\alpha - 3} \int_0^{a_n} \varphi_1(y) e^{-(4\alpha - 2)\frac{y}{2}} 
    	\rho(y,k) \alpha e^{-\alpha y} \dd y\\
	&\le \lim_{n \to \infty} \left(\max_{0 \le y \le a(k)} \varphi_1(y)\right) k^{6\alpha - 1} 
    	\rho(a(k), k) \int_0^\infty \alpha e^{-\alpha y} \dd y = 0.
\end{align*}
For the second integral we first note that due to \eqref{eq:asymptotics_clustering_integral}
\[
	\int_0^\infty e^{-(4\alpha - 2)\frac{y}{2}} \rho(y,k) \alpha e^{-\alpha y} \dd y = \bigT{k^{-(6\alpha - 1)}}.
\] 
Therefore, using that $\varphi_1(y)$ is eventually decreasing and $\lim_{k \to \infty} \varphi_1(a(k)) = 0$, we obtain
\begin{align*}
	&\hspace{-30pt}\lim_{k \to \infty} k^{6\alpha - 3} \int_{a(k)}^{\infty} \varphi_1(y) 
    	e^{-(4\alpha - 2)\frac{y}{2}} \rho(y,k) \alpha e^{-\alpha y} \dd y\\
	&\le \lim_{k \to \infty} \varphi_1(a(k)) k^{6\alpha - 3} \int_0^\infty 
    	e^{-(4\alpha - 2)\frac{y}{2}} \rho(y,k) \alpha e^{-\alpha y} \dd y = 0,
\end{align*}
which finishes the proof.
\end{proof}

@@

We derive the following complete asymptotic expansion of $\Delta_{\Pcal}(y)$, from which then the leading terms can be extracted. The following result proves Proposition \ref{prop:asymptotics_Delta_y_P}, resp. implies it as a corollary after extracting the leading terms.
\begin{proposition}\label{prop:full_expression_delta_P}
\begin{enumerate}
	\item If $\alpha \not = 1$, then
	\begin{align*}
	 \Delta_{\Pcal}(y) &=-\frac{1}{8 (\alpha - 1) \alpha} + \frac{(\alpha - 1/2) e^{-\frac{1}{2}y}}{\alpha - 1} - \frac{(\alpha - 1/2)^2 e^{-y}}{
		4 (\alpha - 1)^2} \\
	&+ 
	(e^{-\frac{1}{2}y})^{4\alpha -2} \left(\frac{2^{-4 \alpha-1} (3 \alpha - 1)}{\alpha (\alpha - 1)^2} + \frac{(\alpha - 
		1/2 ) B^-(1/2; 1 + 2 \alpha, 
		-2 + 2 \alpha)}{2(\alpha - 1) \alpha} \right) \\
	&+ \frac{(1 - 
		e^{-\frac{1}{2}y})^{2 \alpha}}{8 (\alpha - 1) \alpha} - \frac{  
		(e^{-\frac{1}{2}y})^{4 \alpha - 2} B^-(1 - e^{-\frac{1}{2}y}; 2 \alpha, 3 - 4 \alpha)}{4 (\alpha - 1)}
	\end{align*}
	\item If $\alpha = 1$, then
	\begin{align*}
	&\Delta_{\Pcal}(y) =\frac{9}{4} e^{-\frac{1}{2}y} + \frac{1 - 4 e^{-\frac{1}{2}y} + 3 e^{-y}}{4}\ln(1 - e^{-\frac{1}{2}y}) - \frac{7+\pi^2}{8}
e^{-y}  + 
\frac{1}{2}e^{-y}\Li_2(e^{-y})
	\end{align*}
	where $\Li_2(z)=\int_0^z \frac{\ln(1-t)}{t}dt$ is the dipolylogarithm function.
\end{enumerate}
\end{proposition}

@@

For notational convenience we will switch to using $y_0$ instead of $y$. Note that the random variables $Z_i = (x_i,y_i)$, for $i = 1,2$, correspond to first sampling $y_i$ according to the density
\[
	g(y_i) := \left(\alpha -\frac{1}{2}\right) e^{-(\alpha-\frac{1}{2})y_i}
\] 
and then sampling $x_i$ uniformly in $[-e^{\frac{1}{2}(y+y_i)},e^{\frac{1}{2}(y+y_i)}]$. With this in mind we define $P(y_0,y_1,y_2)$ to be the probability that $(0,y_0), (x_1,y_1), (x_2,y_2)$ form a triangle where $x_1$ and $x_2$ are uniform random variables in, respectively, $[-e^{\frac{1}{2}(y_0+y_1)},e^{\frac{1}{2}(y_0+y_1)}]$ and  $[-e^{\frac{1}{2}(y_0+y_2)},e^{\frac{1}{2}(y_0+y_2)}]$.

@@

\subsection{Triangle probability for nodes at given heights}
We proceed by first computing $P(y_0,y_1,y_2)$. To compute the integral~\ref{eq:delta_P} it will be convenient to use the change of variable $z_i = e^{-y_i/2}$, for $i= 0, 1, 2$. We will write $y_i(z_i)$ to stress the dependence between $y_i$ and $z_i$. The following result completely characterizes $P(y_0,y_1,y_2)$.

@@

\begin{proof}
%pim pass1: $P(y_0,y_1,y_2)$ is the probability that $(x_1,y_1)$ and $(x_2,y_2)$ (which are given by a Poisson process in the upper half-plane) are neighbours of each other, given that they are neighbours of $(0,y_0)$ (see figure \ref{fig:triangle_prob_lemma}). By the properties of the Poisson process and our connection rule (which defines the neighourhood area of $(0,y_0)$ in the upper half-plane), given $y_0, y_1, y_2$ we have that $x_i$ is chosen u.a.r.~from $[-e^{y_0/2+y_i/2}, +e^{y_0/2+y_i/2}]$ for $i=1,2$.
Since the Poisson Point Process is translation invariant in the $x$-coordinate we can, without loss of generality, take $x_0 = 0$. By definition of the connection rule $P(y_0,y_1,y_2)$ is the probability that $|x_2-x_1| \leq  e^{(y_1+y_2)/2}$ (see figure \ref{fig:triangle_prob_lemma}). Consider $y_0, y_1, y_2$ and $x_1$ fixed. Then we are interested in computing the probability that $x_2$ falls into the interval $[x_1-e^{(y_1+y+2)/2},x_1+e^{(y_1+y_2)/2}]$ (given by the bottom interval in the Figure~\ref{fig:triangle_prob_lemma}), as well as into the interval $[-e^{(y_0+y_2)/2},e^{(y_0+y_2)/2}]$ (given by the top interval in the Figure~\ref{fig:triangle_prob_lemma}).

@@

\begin{lemma}\label{lem:continuity_Delta_function}
The function $\alpha \mapsto \Delta_{\Pcal_{\alpha,\nu}}(y_0)$ is continuous for all $\alpha > \frac{1}{2}$.
\end{lemma}
\begin{proof}
This follows from the theorem of dominated convergence:
Let $\alpha > \frac{1}{2}$ and $(\alpha_n)_{n\in \mathbb{N}}$ a sequence of real numbers converging to $\alpha$, so we can assume $|\alpha_n - \alpha| < \epsilon := \frac{\alpha-1/2}{2}$. This means that $-\epsilon < \alpha_n - \alpha < \epsilon$, i.e. $\frac{\alpha-1/2}{2} < \alpha_n - 1/2 < \frac{3\alpha-3/2}{2}$. Define $f_n(y_1,y_2) = P(y_0,y_1,y_2) (\alpha_n - 1/2)^2 e^{-(\alpha_n-1/2)(y_1+y_2)}$. As the function $x \mapsto x^2$ is increasing in $x$ for $x>0$ and the function $x \mapsto e^{-(y_1+y_2)x}$ is decreasing in $x$ and $P(y_0,y_1,y_2) \in [0,1]$, it holds that $|f_n(y_1,y_2)| \leq (\frac{3\alpha-3/2}{2})^2e^{-(y_1+y_2)\frac{\alpha-1/2}{2}}$ which is integrable over $\R_{\geq 0} \times \R_{\geq 0}$ (with integral equals $\frac{(6\alpha-3)^2}{(2\alpha-1)^2}$). Application of the theorem of dominated convergence and using equation~\eqref{eq:def_delta_p} yields that $\Delta_{\Pcal_{\alpha_n,\nu}}(y_0) \rightarrow \Delta_{\Pcal_{\alpha,\nu}}(y_0)$ which gives the claim as the sequence $(\alpha_n)_n$ was arbitrary.
\end{proof}

@@

To deal with $I_{12}$ we note that $G(z_0,z_1,z_2)$ is a linear combination of monomials of the form $z_0^az_1^bz_2^c$ with 
$a,b,c \in \{-1,0,1,2\}$ and $a+b+c=0$. Let us consider the integral $J_(a,b,c)(z_0)$
\begin{equation}\label{eq:def_Delta_P_computation_int_J_1}
	J_{a,b,c}(z_0) := z_0^a \int_{{z_0>z_1>z_2>0,}\atop{z_0 < z_1+z_2}} z_1^{b+2\alpha-2} z_2^{c+2\alpha-2} {\dd}z_2{\dd}z_1.
\end{equation}
and note that
\begin{equation}\label{eq:Delta_P_computation_I12_with_J}
	I_{1,2}(y_0) = \frac{1}{4} (J_{0,-1,1}(z_0)+J_{0,1,-1}(z_0)+J_{2,-1,-1}(z_0)+2J_{0,0,0}(z_0)-2J_{1,-1,0}(z_0)-2J_{1,0,-1}(z_0)).
\end{equation}

>>>>

\TM{ @Pim and @Nikolaos : if you have not done so already, can you please check the computations in section 4 very very carefully. }
In this section we will establish the exact expressions for the limit local clustering coefficient and function, $c_\Pcal$ and $c_{\Pcal}(k)$, respectively. This is done in several steps. Recall that for $p\in \R \times \R_+ =: \Rcal$,
\[
	\BallPo{p} = \{p^\prime \in \R \times \R_+ : |x - x^\prime| \le e^{\frac{y + y^\prime}{2}}\},
\]
denotes the neighborhood ball of $p$. Furthermore we recall the definition of $\Delta_\Pcal$ 
\[
	\Delta_{\Pcal}(y) = \iint_{\Rcal^2} T_\Pcal(p,p_1,p_2) \eta_{y}(x_1,y_1)\eta_{y}(x_2,y_2) \, dx1 \, dx_2 \, dy_1 \, dy_2,
\]
where $\eta_{y} = \frac{\mu_{\alpha,\nu}|_{\BallPo{(0,y)}}}{\Mu{\BallPo{(0,y)}}}$ is the marginal probability density associated with a randomly sampled neighbor of $(0,y)$.

@@

Before we analyze local clustering in the infinite limit model, we first establish some results for its degree distribution. \TM{ like "randomly sampled", "degree distribution" is a weird concept for infinite graphs. Not sure it even makes sense. Better to speak of "degree of a typical node", i.e. $x=0$ and $y$ is exponential $\alpha$, independent of the PPP.} We define the probability distribution for the degree of node $p = (x,y)$ \TM{ Indeed, for clarity, we ought to add we add the point $p$ to the PPP, and then study its degree. } as
\begin{equation}
	\rho(p,k) = \Prob{D_\Pcal(p) = k} = \Prob{\Po(\mu_{\alpha,\nu}(\BallPo{p})) = k},
\end{equation}
where $\Po(\lambda)$ denotes a Poisson random variable with mean $\lambda$. Recall from equation \eqref{eq:mu_ball_y_P} that
\[
	\mu_{\alpha,\nu}(\BallPo{p}) = \xi_{\alpha,\nu} e^{\frac{y}{2}},
\]
only depends on the $y$-coordinate of $p$. Therefore, we will often write $\rho(y,k)$ instead of $\rho(p,k)$.

@@

Since $\Gamma^{+}(k-2\alpha, \xi_{\alpha,\nu})/\Gamma(k - 2\alpha) \sim k^{-(2\alpha+1)}$ as $k \to \infty$
\TM{ Typo, bottom should be $\Gamma(k+1)$. } \PvdH{@All: Does anyone have a good standard reference for this?} 
\TM{ This follows from Stirling's approx, which works also for non-integer values, together with the obvious fact that $\lim_{x\to\infty} \Gamma^x(x,c) / \Gamma(x) = 1$ and some obvious manipulations. We ought to provide reference + explanation though. Ref for the Stirling approx : De Bruijn, "asymptotic methods in analysis", 3rd edition, section 4.5 } we deduce that
\begin{equation}\label{eq:degree_distribution_P_asymptotics}
	\Prob{D_\Pcal = k} \sim 2\alpha (\xi_{\alpha,\nu})^{2\alpha} k^{-(2\alpha + 1)}
	\quad \text{as } k \to \infty.
\end{equation}

By a similar computation we have the following result, which will be useful later on. For any $\beta > 0$, as $k \to \infty$
\begin{equation}\label{eq:general_integral_rho_y_k}
	\int_0^\infty e^{\beta y} \rho_y(k) \alpha e^{-\alpha y} \, dy
    \sim 2\alpha \left(\xi_{\alpha,\nu}\right)^{2(\beta + \alpha)} k^{-2(\beta + \alpha)-1}.
\end{equation}
\TM{ $y$ is a subscript here, but is an argument just above. Maybe stick with having it as an argument. }

@@

The proof of this proposition is involved and technical. We therefore postpone it till Section \ref{ssec:asymptotics_Delta_y_P} \TM{ It is not in section 4.3!!!! IN fact I cannot find it in sec 4 alltogether. Please fix. We do need this worked out explicitly in the paper. } and first use it to prove Theorem \ref{thm:asymptotics_average_clustering_P}.

@@

We only give the proof for the case $\frac{1}{2} < \alpha < \frac{3}{4}$. \TM{ not sure I am happy with this "other cases are similar" approach. Especially in a 100 page paper. The devil is in the details! } The proofs for the other two cases are similar. Let $\varphi_1(y)$ be defined as in Proposition \ref{prop:asymptotics_Delta_y_P} and define
\[
	\epsilon_1(k) = \int_0^{\infty} \varphi_1(y) e^{-(4\alpha - 2)\frac{y}{2}} \rho(y,k) \alpha e^{-\alpha y} \dd y
\]
Then we have that
\[
	\int_0^{\infty} \Delta_{\mathcal{P}}(y) \rho(y,k) \alpha e^{-\alpha y} \dd y
	= C_\alpha \int_0^{\infty} e^{-(4\alpha - 2)\frac{y}{2}} \rho(y,k) \alpha e^{-\alpha y} \dd y + \epsilon_1(k).
\]

Using \eqref{eq:general_integral_rho_y_k} with $\beta = 2\alpha - 1$ yields,
\begin{equation}\label{eq:asymptotics_clustering_integral}
	\int_0^{\infty} e^{-(4\alpha - 2)\frac{y}{2}} \rho(y,k) \alpha e^{-\alpha y} \dd y 
	\sim 2\alpha \xi_{\alpha,\nu}^{6\alpha - 2} k^{-(6\alpha - 1)},
\end{equation}
as $k \to \infty$. Therefore, by applying the asymptotic scaling for the denominator~\eqref{eq:degree_distribution_P_asymptotics} we get
\begin{align*}
	c_\infty(k) &= \frac{\int_0^{\infty} \Delta_{\mathcal{P}}(y) \rho(y,k) \alpha  e^{-\alpha y} \dd y}
		{\int_0^\infty \rho_{y}(k) \alpha e^{-\alpha y} \dd y} \\
	&\sim C_\alpha 2\alpha \xi_{\alpha,\nu}^{4\alpha - 2} \frac{k^{-(6\alpha - 1)}}{k^{-(2\alpha - 1)}}
	+ \frac{\epsilon_1(k)}{2\alpha \xi_{\alpha,\nu}^{2\alpha} k^{-(2\alpha - 1)}}\\
	&= C_\alpha 2\alpha \xi_{\alpha,\nu}^{4\alpha - 2} k^{-4\alpha + 2} 
    + \frac{1}{2\alpha}\xi_{\alpha,\nu}^{-2\alpha} k^{2\alpha - 1}\epsilon_1(k).
\end{align*}
Hence, to prove the result it is enough to show that
\[
	\lim_{k \to \infty} k^{6\alpha - 3}\epsilon_1(k) = 0.
\]
For this we fix $0 < \varphi < 1$, define $a(k) = 2\log((1-\varphi)k)$ \TM{ should there not be a $k/\xi$ inside $\log$ here? (see below) } and split the integral into two pieces
\begin{align*}
	\epsilon_1(k) &= \int_0^{\infty} \varphi_1(y) e^{-(4\alpha - 2)\frac{y}{2}} \rho(y,k) \alpha e^{-\alpha y} \dd y\\
	&= \int_0^{a(k)} \varphi_1(y) e^{-(4\alpha - 2)\frac{y}{2}} \rho(y,k) \alpha e^{-\alpha y} \dd y\\
	&\hspace{10pt}+ \int_{a(k)}^{\infty} \varphi_1(y) e^{-(4\alpha - 2)\frac{y}{2}} 
    	\rho(y,k) \alpha e^{-\alpha y} \dd y.
\end{align*} 
For the first integral we use that $\rho(y,k)$ is increasing on $[0,a(k)]$ \TM{ I think that is only true if we change the def as above, in accordance with $a^{\pm}$ earlier. } and
\[
	k^{6\alpha - 3}\rho(a(k),k) = O\left(\frac{k^{6\alpha - 3 + (1-\varphi)k}}{k!} e^{-(1-\varphi)k}\right) = o(1),
\]
\TM{ again, it seems off. I think we need to take $\xi$ into account here. }
to obtain
\begin{align*}
	&\hspace{-30pt}\lim_{k \to \infty} k^{6\alpha - 3} \int_0^{a_n} \varphi_1(y) e^{-(4\alpha - 2)\frac{y}{2}} 
    	\rho(y,k) \alpha e^{-\alpha y} \dd y\\
	&\le \lim_{n \to \infty} \left(\max_{0 \le y \le a(k)} \varphi_1(y)\right) k^{6\alpha - 1} 
    	\rho(a(k), k) \int_0^\infty \alpha e^{-\alpha y} \dd y = 0.
\end{align*}
For the second integral we first note that due to \eqref{eq:asymptotics_clustering_integral}
\[
	\int_0^\infty e^{-(4\alpha - 2)\frac{y}{2}} \rho(y,k) \alpha e^{-\alpha y} \dd y = \bigT{k^{-(6\alpha - 1)}}.
\] 
Therefore, using that $\varphi_1(y)$ is eventually decreasing and $\lim_{k \to \infty} \varphi_1(a(k)) = 0$, we obtain
\begin{align*}
	&\hspace{-30pt}\lim_{k \to \infty} k^{6\alpha - 3} \int_{a(k)}^{\infty} \varphi_1(y) 
    	e^{-(4\alpha - 2)\frac{y}{2}} \rho(y,k) \alpha e^{-\alpha y} \dd y\\
	&\le \lim_{k \to \infty} \varphi_1(a(k)) k^{6\alpha - 3} \int_0^\infty 
    	e^{-(4\alpha - 2)\frac{y}{2}} \rho(y,k) \alpha e^{-\alpha y} \dd y = 0,
\end{align*}
which finishes the proof. \TM{ PLease elaborate on last line. What is used here? }
\end{proof}

@@

We derive the following explicit expression for $\Delta_{\Pcal}(y)$, from which then the leading terms can be extracted. The following result proves Proposition \ref{prop:asymptotics_Delta_y_P}, resp. implies it as a corollary after extracting the leading terms. \TM{ Extracting the leading terms needs to be done explicitly in the paper! If it is already in the paper somewhere, add explicit reference. }

\begin{proposition}\label{prop:full_expression_delta_P}
\begin{enumerate}
	\item If $\alpha \not = 1$, then
	\begin{align*}
	 \Delta_{\Pcal}(y) &=-\frac{1}{8 (\alpha - 1) \alpha} + \frac{(\alpha - 1/2) e^{-\frac{1}{2}y}}{\alpha - 1} - \frac{(\alpha - 1/2)^2 e^{-y}}{
		4 (\alpha - 1)^2} \\
	&+ 
	(e^{-\frac{1}{2}y})^{4\alpha -2} \left(\frac{2^{-4 \alpha-1} (3 \alpha - 1)}{\alpha (\alpha - 1)^2} + \frac{(\alpha - 
		1/2 ) B^-(1/2; 1 + 2 \alpha, 
		-2 + 2 \alpha)}{2(\alpha - 1) \alpha} \right) \\
	&+ \frac{(1 - 
		e^{-\frac{1}{2}y})^{2 \alpha}}{8 (\alpha - 1) \alpha} - \frac{  
		(e^{-\frac{1}{2}y})^{4 \alpha - 2} B^-(1 - e^{-\frac{1}{2}y}; 2 \alpha, 3 - 4 \alpha)}{4 (\alpha - 1)}
	\end{align*}
	\item If $\alpha = 1$, then
	\begin{align*}
	&\Delta_{\Pcal}(y) =\frac{9}{4} e^{-\frac{1}{2}y} + \frac{1 - 4 e^{-\frac{1}{2}y} + 3 e^{-y}}{4}\ln(1 - e^{-\frac{1}{2}y}) - \frac{7+\pi^2}{8}
e^{-y}  + 
\frac{1}{2}e^{-y}\Li_2(e^{-y})
	\end{align*}
	where $\Li_2(z)=\int_0^z \frac{\ln(1-t)}{t}dt$ is the dipolylogarithm function.
\end{enumerate}
\end{proposition}

@@

For notational convenience we will switch to using $y_0$ instead of $y$. Note that the random variables $Z_i = (x_i,y_i)$, for $i = 1,2$, correspond to first sampling $y_i$ according to the density
\[
	g(y_i) := \left(\alpha -\frac{1}{2}\right) e^{-(\alpha-\frac{1}{2})y_i}
\] 
and then sampling $x_i$ uniformly in $[-e^{\frac{1}{2}(y+y_i)},e^{\frac{1}{2}(y+y_i)}]$. With this in mind we define $P(y_0,y_1,y_2)$ to be the probability that $(0,y_0), (x_1,y_1), (x_2,y_2)$ form a triangle where $x_1$ and $x_2$ are independent uniform random variables in, respectively, $[-e^{\frac{1}{2}(y_0+y_1)},e^{\frac{1}{2}(y_0+y_1)}]$ and  $[-e^{\frac{1}{2}(y_0+y_2)},e^{\frac{1}{2}(y_0+y_2)}]$.

@@

\subsection{Triangle probability for nodes at given heights}
We proceed by first computing $P(y_0,y_1,y_2)$. To compute the integral~\eqref{eq:delta_P} it will be convenient to use the change of variable $z_i = e^{-y_i/2}$, for $i= 0, 1, 2$. We will write $y_i(z_i)$ to stress the dependence between $y_i$ and $z_i$. The following result completely characterizes $P(y_0,y_1,y_2)$.

@@

\begin{proof}
%pim pass1: $P(y_0,y_1,y_2)$ is the probability that $(x_1,y_1)$ and $(x_2,y_2)$ (which are given by a Poisson process in the upper half-plane) are neighbours of each other, given that they are neighbours of $(0,y_0)$ (see figure \ref{fig:triangle_prob_lemma}). By the properties of the Poisson process and our connection rule (which defines the neighourhood area of $(0,y_0)$ in the upper half-plane), given $y_0, y_1, y_2$ we have that $x_i$ is chosen u.a.r.~from $[-e^{y_0/2+y_i/2}, +e^{y_0/2+y_i/2}]$ for $i=1,2$.
Since the Poisson Point Process is translation invariant in the $x$-coordinate we can, without loss of generality, take $x_0 = 0$. \TM{ Sentence does not fit with previous discussion, we already said we took $(0,y_0)$ as the central point. } By definition of the connection rule $P(y_0,y_1,y_2)$ is the probability that $|x_2-x_1| \leq  e^{(y_1+y_2)/2}$ (see figure \ref{fig:triangle_prob_lemma}). Consider $y_0, y_1, y_2$ and $x_1$ fixed. Then we are interested in computing the probability that $x_2$ falls into the interval $[x_1-e^{(y_1+y_2)/2},x_1+e^{(y_1+y_2)/2}]$ (given by the bottom interval in the Figure~\ref{fig:triangle_prob_lemma}), as well as into the interval $[-e^{(y_0+y_2)/2},e^{(y_0+y_2)/2}]$ (given by the top interval in the Figure~\ref{fig:triangle_prob_lemma}).

@@

\begin{lemma}\label{lem:continuity_Delta_function}
The function $\alpha \mapsto \Delta_{\Pcal_{\alpha,\nu}}(y_0)$ is continuous for all $\alpha > \frac{1}{2}$.
\end{lemma}

\begin{proof}
This follows from the theorem of dominated convergence:
Let $\alpha > \frac{1}{2}$ and $(\alpha_n)_{n\in \mathbb{N}}$ a sequence of real numbers converging to $\alpha$, so we can assume $|\alpha_n - \alpha| < \epsilon := \frac{\alpha-1/2}{2}$. This means that $-\epsilon < \alpha_n - \alpha < \epsilon$, i.e. $\frac{\alpha-1/2}{2} < \alpha_n - 1/2 < \frac{3\alpha-3/2}{2}$. Define

$$f_n(y_1,y_2) = P(y_0,y_1,y_2) (\alpha_n - 1/2)^2 e^{-(\alpha_n-1/2)(y_1+y_2)}.$$

As the function $x \mapsto x^2$ is increasing in $x$ for $x>0$ and the function $x \mapsto e^{-(y_1+y_2)x}$ is decreasing in $x$ and $P(y_0,y_1,y_2) \in [0,1]$, it holds that

$$|f_n(y_1,y_2)| \leq \left(\frac{3\alpha-3/2}{2}\right)^2e^{-(y_1+y_2)\frac{\alpha-1/2}{2}}$$

which is integrable over $\R_{\geq 0} \times \R_{\geq 0}$ (with integral equalling $(6\alpha-3)^2/(2\alpha-1)^2$). Application of the theorem of dominated convergence and using equation~\eqref{eq:def_delta_p} yields that $\Delta_{\Pcal_{\alpha_n,\nu}}(y_0) \rightarrow \Delta_{\Pcal_{\alpha,\nu}}(y_0)$ which gives the claim as the sequence $(\alpha_n)_n$ was arbitrary.
\end{proof}

@@

To deal with $I_{12}$ we note that $G(z_0,z_1,z_2)$ is a linear combination of monomials of the form $z_0^az_1^bz_2^c$ with 
$a,b,c \in \{-1,0,1,2\}$ and $a+b+c=0$. Let us consider the integral $J_{(a,b,c)}(z_0)$ defined by

\begin{equation}\label{eq:def_Delta_P_computation_int_J_1}
	J_{a,b,c}(z_0) := z_0^a \int_{{z_0>z_1>z_2>0,}\atop{z_0 < z_1+z_2}} z_1^{b+2\alpha-2} z_2^{c+2\alpha-2} {\dd}z_2{\dd}z_1.
\end{equation}
and note that
\begin{equation}\label{eq:Delta_P_computation_I12_with_J}
	I_{1,2}(y_0) = \frac{1}{4} (J_{0,-1,1}(z_0)+J_{0,1,-1}(z_0)+J_{2,-1,-1}(z_0)+2J_{0,0,0}(z_0)-2J_{1,-1,0}(z_0)-2J_{1,0,-1}(z_0)).
\end{equation}
